### 2013-09-27 manuscripts/dpp-msbayes/dpp-msbayes.tex
Adding many more figures to dpp ms.

>>>>

%% Power accuracy results
\mFigure{../../power-comparison/results/pymsbayes-results/plots/exp_dpp_power_accuracy_omega_median.pdf}{
    \powerAccuracyCaption{\powerSeriesUniformExp}{\modelDPP}
}{figPowerAccuracyUniformExpDPP}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/exp_uniform_power_accuracy_omega_median.pdf}{
    \powerAccuracyCaption{\powerSeriesUniformExp}{\modelUniform}
}{figPowerAccuracyUniformExpUniform}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/exp_old_power_accuracy_omega_median.pdf}{
    \powerAccuracyCaption{\powerSeriesUniformExp}{\modelOld}
}{figPowerAccuracyUniformExpOld}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/exp_u-shaped_power_accuracy_omega_median.pdf}{
    \powerAccuracyCaption{\powerSeriesUniformExp}{\modelUshaped}
}{figPowerAccuracyUniformExpUshaped}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/uniform_dpp_power_accuracy_omega_median.pdf}{
    \powerAccuracyCaption{\powerSeriesUniform}{\modelDPP}
}{figPowerAccuracyUniformDPP}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/uniform_uniform_power_accuracy_omega_median.pdf}{
    \powerAccuracyCaption{\powerSeriesUniform}{\modelUniform}
}{figPowerAccuracyUniformUniform}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/uniform_old_power_accuracy_omega_median.pdf}{
    \powerAccuracyCaption{\powerSeriesUniform}{\modelOld}
}{figPowerAccuracyUniformOld}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/uniform_u-shaped_power_accuracy_omega_median.pdf}{
    \powerAccuracyCaption{\powerSeriesUniform}{\modelUshaped}
}{figPowerAccuracyUniformUshaped}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/old_dpp_power_accuracy_omega_median.pdf}{
    \powerAccuracyCaption{\powerSeriesOld}{\modelDPP}
}{figPowerAccuracyOldDPP}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/old_uniform_power_accuracy_omega_median.pdf}{
    \powerAccuracyCaption{\powerSeriesOld}{\modelUniform}
}{figPowerAccuracyOldUniform}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/old_old_power_accuracy_omega_median.pdf}{
    \powerAccuracyCaption{\powerSeriesOld}{\modelOld}
}{figPowerAccuracyOldOld}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/old_u-shaped_power_accuracy_omega_median.pdf}{
    \powerAccuracyCaption{\powerSeriesOld}{\modelUshaped}
}{figPowerAccuracyOldUshaped}

%% Power psi results
\mFigure{../../power-comparison/results/pymsbayes-results/plots/exp_dpp_power_psi_mode.pdf}{
    \powerPsiCaption{\powerSeriesUniformExp}{\modelDPP}
}{figPowerPsiUniformExpDPP}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/exp_uniform_power_psi_mode.pdf}{
    \powerPsiCaption{\powerSeriesUniformExp}{\modelUniform}
}{figPowerPsiUniformExpUniform}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/exp_old_power_psi_mode.pdf}{
    \powerPsiCaption{\powerSeriesUniformExp}{\modelOld}
}{figPowerPsiUniformExpOld}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/exp_u-shaped_power_psi_mode.pdf}{
    \powerPsiCaption{\powerSeriesUniformExp}{\modelUshaped}
}{figPowerPsiUniformExpUshaped}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/uniform_dpp_power_psi_mode.pdf}{
    \powerPsiCaption{\powerSeriesUniform}{\modelDPP}
}{figPowerPsiUniformDPP}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/uniform_uniform_power_psi_mode.pdf}{
    \powerPsiCaption{\powerSeriesUniform}{\modelUniform}
}{figPowerPsiUniformUniform}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/uniform_old_power_psi_mode.pdf}{
    \powerPsiCaption{\powerSeriesUniform}{\modelOld}
}{figPowerPsiUniformOld}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/uniform_u-shaped_power_psi_mode.pdf}{
    \powerPsiCaption{\powerSeriesUniform}{\modelUshaped}
}{figPowerPsiUniformUshaped}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/old_dpp_power_psi_mode.pdf}{
    \powerPsiCaption{\powerSeriesOld}{\modelDPP}
}{figPowerPsiOldDPP}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/old_uniform_power_psi_mode.pdf}{
    \powerPsiCaption{\powerSeriesOld}{\modelUniform}
}{figPowerPsiOldUniform}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/old_old_power_psi_mode.pdf}{
    \powerPsiCaption{\powerSeriesOld}{\modelOld}
}{figPowerPsiOldOld}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/old_u-shaped_power_psi_mode.pdf}{
    \powerPsiCaption{\powerSeriesOld}{\modelUshaped}
}{figPowerPsiOldUshaped}

%% Power dispersion results
\mFigure{../../power-comparison/results/pymsbayes-results/plots/exp_dpp_power_omega_median.pdf}{
    \powerDispersionCaption{\powerSeriesUniformExp}{\modelDPP}
}{figPowerDispersionUniformExpDPP}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/exp_uniform_power_omega_median.pdf}{
    \powerDispersionCaption{\powerSeriesUniformExp}{\modelUniform}
}{figPowerDispersionUniformExpUniform}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/exp_old_power_omega_median.pdf}{
    \powerDispersionCaption{\powerSeriesUniformExp}{\modelOld}
}{figPowerDispersionUniformExpOld}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/exp_u-shaped_power_omega_median.pdf}{
    \powerDispersionCaption{\powerSeriesUniformExp}{\modelUshaped}
}{figPowerDispersionUniformExpUshaped}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/uniform_dpp_power_omega_median.pdf}{
    \powerDispersionCaption{\powerSeriesUniform}{\modelDPP}
}{figPowerDispersionUniformDPP}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/uniform_uniform_power_omega_median.pdf}{
    \powerDispersionCaption{\powerSeriesUniform}{\modelUniform}
}{figPowerDispersionUniformUniform}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/uniform_old_power_omega_median.pdf}{
    \powerDispersionCaption{\powerSeriesUniform}{\modelOld}
}{figPowerDispersionUniformOld}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/uniform_u-shaped_power_omega_median.pdf}{
    \powerDispersionCaption{\powerSeriesUniform}{\modelUshaped}
}{figPowerDispersionUniformUshaped}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/old_dpp_power_omega_median.pdf}{
    \powerDispersionCaption{\powerSeriesOld}{\modelDPP}
}{figPowerDispersionOldDPP}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/old_uniform_power_omega_median.pdf}{
    \powerDispersionCaption{\powerSeriesOld}{\modelUniform}
}{figPowerDispersionOldUniform}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/old_old_power_omega_median.pdf}{
    \powerDispersionCaption{\powerSeriesOld}{\modelOld}
}{figPowerDispersionOldOld}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/old_u-shaped_power_omega_median.pdf}{
    \powerDispersionCaption{\powerSeriesOld}{\modelUshaped}
}{figPowerDispersionOldUshaped}

%% Power psi probability results
\mFigure{../../power-comparison/results/pymsbayes-results/plots/exp_dpp_power_psi_prob.pdf}{
    \powerPsiProbCaption{\powerSeriesUniformExp}{\modelDPP}
}{figPowerPsiProbUniformExpDPP}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/exp_uniform_power_psi_prob.pdf}{
    \powerPsiProbCaption{\powerSeriesUniformExp}{\modelUniform}
}{figPowerPsiProbUniformExpUniform}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/exp_old_power_psi_prob.pdf}{
    \powerPsiProbCaption{\powerSeriesUniformExp}{\modelOld}
}{figPowerPsiProbUniformExpOld}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/exp_u-shaped_power_psi_prob.pdf}{
    \powerPsiProbCaption{\powerSeriesUniformExp}{\modelUshaped}
}{figPowerPsiProbUniformExpUshaped}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/uniform_dpp_power_psi_prob.pdf}{
    \powerPsiProbCaption{\powerSeriesUniform}{\modelDPP}
}{figPowerPsiProbUniformDPP}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/uniform_uniform_power_psi_prob.pdf}{
    \powerPsiProbCaption{\powerSeriesUniform}{\modelUniform}
}{figPowerPsiProbUniformUniform}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/uniform_old_power_psi_prob.pdf}{
    \powerPsiProbCaption{\powerSeriesUniform}{\modelOld}
}{figPowerPsiProbUniformOld}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/uniform_u-shaped_power_psi_prob.pdf}{
    \powerPsiProbCaption{\powerSeriesUniform}{\modelUshaped}
}{figPowerPsiProbUniformUshaped}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/old_dpp_power_psi_prob.pdf}{
    \powerPsiProbCaption{\powerSeriesOld}{\modelDPP}
}{figPowerPsiProbOldDPP}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/old_uniform_power_psi_prob.pdf}{
    \powerPsiProbCaption{\powerSeriesOld}{\modelUniform}
}{figPowerPsiProbOldUniform}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/old_old_power_psi_prob.pdf}{
    \powerPsiProbCaption{\powerSeriesOld}{\modelOld}
}{figPowerPsiProbOldOld}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/old_u-shaped_power_psi_prob.pdf}{
    \powerPsiProbCaption{\powerSeriesOld}{\modelUshaped}
}{figPowerPsiProbOldUshaped}

%% Power dispersion prob results
\mFigure{../../power-comparison/results/pymsbayes-results/plots/exp_dpp_power_omega_prob.pdf}{
    \powerDispersionProbCaption{\powerSeriesUniformExp}{\modelDPP}
}{figPowerDispersionProbUniformExpDPP}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/exp_uniform_power_omega_prob.pdf}{
    \powerDispersionProbCaption{\powerSeriesUniformExp}{\modelUniform}
}{figPowerDispersionProbUniformExpUniform}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/exp_old_power_omega_prob.pdf}{
    \powerDispersionProbCaption{\powerSeriesUniformExp}{\modelOld}
}{figPowerDispersionProbUniformExpOld}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/exp_u-shaped_power_omega_prob.pdf}{
    \powerDispersionProbCaption{\powerSeriesUniformExp}{\modelUshaped}
}{figPowerDispersionProbUniformExpUshaped}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/uniform_dpp_power_omega_prob.pdf}{
    \powerDispersionProbCaption{\powerSeriesUniform}{\modelDPP}
}{figPowerDispersionProbUniformDPP}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/uniform_uniform_power_omega_prob.pdf}{
    \powerDispersionProbCaption{\powerSeriesUniform}{\modelUniform}
}{figPowerDispersionProbUniformUniform}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/uniform_old_power_omega_prob.pdf}{
    \powerDispersionProbCaption{\powerSeriesUniform}{\modelOld}
}{figPowerDispersionProbUniformOld}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/uniform_u-shaped_power_omega_prob.pdf}{
    \powerDispersionProbCaption{\powerSeriesUniform}{\modelUshaped}
}{figPowerDispersionProbUniformUshaped}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/old_dpp_power_omega_prob.pdf}{
    \powerDispersionProbCaption{\powerSeriesOld}{\modelDPP}
}{figPowerDispersionProbOldDPP}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/old_uniform_power_omega_prob.pdf}{
    \powerDispersionProbCaption{\powerSeriesOld}{\modelUniform}
}{figPowerDispersionProbOldUniform}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/old_old_power_omega_prob.pdf}{
    \powerDispersionProbCaption{\powerSeriesOld}{\modelOld}
}{figPowerDispersionProbOldOld}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/old_u-shaped_power_omega_prob.pdf}{
    \powerDispersionProbCaption{\powerSeriesOld}{\modelUshaped}
}{figPowerDispersionProbOldUshaped}

### 2013-09-27 manuscripts/utils/macros.tex
Adding many more figures to dpp ms.

\newcommand{\validationAccuracyCaption}[2]{Estimation accuracy for model
    #1 when analyzing data generated under #2.
    A random sample of 5000 posterior estimates (from 50,000) are plotted,
    including both (A, B, \& C) unadjusted and (D, E, \&
    F) GLM-regression-adjusted estimates.
    Normal random variates ($N(0, 0.005)$) have been added to the estimates and
    true values of \divTimeNum (A \& D) to reduce overlap of plot symbols.
    The root mean square error (RMSE) calculated from the 5000 estimates is
    provided.}
\newcommand{\simulationDescription}[2]{\change{Each plot represents #1
    simulation replicates using the same $#2$ samples from the prior}}
\newcommand{\simulationDistribution}{\ensuremath{\divt{} \sim U(0,
    \divt{max})}\xspace}
\newcommand{\estimateDescription}[2]{All estimates were obtained using #1 and #2}
\newcommand{\estimateDescriptionUncorrected}[1]{All estimates based on
    unadjusted posterior, \truncprior{}, obtained using #1}
\newcommand{\priorDescription}[4]{Prior settings were \priorSettings{#1}{#2}{#3}{#4}}
\newcommand{\priorSettings}[4]{$\divt{} \sim U(0, #1)$,
    $\meanDescendantTheta{} \sim U(#2, #3)$, and
    $\ancestralTheta{}{} \sim U(#2, #4)$}
\newcommand{\priorDescriptionBug}[4]{Prior settings were
    \priorSettingsBug{#1}{#2}{#3}{#4}}
\newcommand{\priorSettingsBug}[4]{$\divt{} \sim U(0, #1)$,
    $\meanDescendantTheta{} \sim U(#2, #3)$, and
    $\ancestralTheta{}{} \sim U(0.01, #4)$}
\newcommand{\simulationScheme}{simulations where \divt{} (in \globalcoalunit
    generations) for 22 population pairs is drawn from a series of uniform
    distributions, \simulationDistribution}
\newcommand{\captionPowerOmega}{Histograms of the estimated dispersion index
    of divergence times ($\hat{\vmratio{}}$) from \simulationScheme.
    The threshold for one divergence event \citep{Hickerson2006} is indicated
    by the dashed line, and the estimated probability of inferring one
    divergence event, $p(\hat{\vmratio{}}\le 0.01)$, is given for each
    \divt{max}}
\newcommand{\captionPowerPsiMode}{Histograms of the estimated number of
    divergence events ($\hat{\numt{}}$) from \simulationScheme.
    The estimated probability of inferring one divergence event,
    $p(\hat{\numt{}} = 1)$, is given for each \divt{max}}
\newcommand{\captionPowerPsi}{Histograms of the estimated posterior
    probability of one divergence event, \postprobnumt{1}, from
    \simulationScheme.
    The estimated probability of inferring one divergence event with a
    Bayes factor greater than 10 (dashed black line),
    $p(\bayesfactor{\numt{}=1}{\numt{} \ne 1} > 10)$, is given for each \divt{max}.
    The red line indicates $\postprobnumt{1} = 0.95$, and the estimated
    probability of inferring a posterior probability greater than 0.95 is given
    to the right of the line.}
\newcommand{\captionAccuracy}[1]{Accuracy and precision of #1 estimates from
    \simulationScheme.
    The proportion of estimates less than the true value ($p(\hat{#1}<#1)$) is
    given for each \divt{max}}
\newcommand{\samplingErrorTableNote}{An estimate of 1.0 for a posterior probability
    is an artifact of sampling error}

>>>>

\newcommand{\validationAccuracyCaption}[2]{Estimation accuracy for model
    #2 when analyzing data generated under #1.
    A random sample of 5000 posterior estimates (from 50,000) are plotted,
    including both (A, B, \& C) unadjusted and (D, E, \&
    F) GLM-regression-adjusted estimates.
    Normal random variates ($N(0, 0.005)$) have been added to the estimates and
    true values of \divTimeNum (A \& D) to reduce overlap of plot symbols.
    The root mean square error (RMSE) calculated from the 5000 estimates is
    provided.}
\newcommand{\validationModelChoiceCaption}[2]{Model-choice accuracy for model
    #2 when analyzing data generated under #1.
    The estimated posterior probability of a single divergence event, based on
    (A \& C) $\divTimeNum = 1$ and (B \& D) $\divTimeDispersion < 0.01$, from
    50,000 posterior estimates are assigned to bins of width 0.05 and plotted
    against the proportion of replicates in each bin where the truth is
    $\divTimeNum = 1$ or $\divTimeDispersion < 0.01$.
    Results based on the (A \& B) unadjusted and (C \& D) GLM-adjusted
    posterior estimates are shown.}
\newcommand{\powerAccuracyCaption}[2]{Estimation accuracy for model
    #2 when analyzing data generated under the series of models #1.
    The true versus estimated value of the dispersion index of divergence
    times (\divTimeDispersion) is plotted for 1000 datasets simulated
    under each of the #1 models, and the proportion of estimates less
    than the truth, $p(\hat{\divTimeDispersion} < \divTimeDispersion)$,
    is shown for each data model.}
\newcommand{\powerPsiCaption}[2]{
    The power of model #2 to detect random variation in divergence times as
    simulated under the series of models #1.
    The plots illustrate the estimated number of divergence events
    ($\hat{\divTimeNum}$) from analyses of 1000 datasets simulated under each
    of the #1 models, with the the estimated probability of the model inferring
    one divergence event, $p(\hat{\divTimeNum} = 1)$, given for each data
    model.}
\newcommand{\powerDispersionCaption}[2]{
    The power of model #2 to detect random variation in divergence times as
    simulated under the series of models #1.
    The plots illustrate the estimated dispersion index of divergence times
    ($\hat{\divTimeDispersion}$) from analyses of 1000 datasets simulated under
    each of the #1 models, with the the estimated probability of the model
    inferring one divergence event, $p(\hat{\divTimeDispersion} < 0.01)$, given
    for each data model.}
\newcommand{\powerPsiProbCaption}[2]{
    The tendency of model #2 to support one divergence event when there is
    random variation in divergence times as simulated under the series of
    models #1.
    The plots illustrate histograms of the estimated posterior probability of
    the one divergence model, $p(\divTimeNum = 1 | \ssSpace)$, from analyses of
    1000 datasets simulated under each of the #1 models, with the the estimated
    probability of the model strongly supporting one divergence event,
    $p(BF_{\divTimeNum = 1, \divTimeNum \neq 1} > 10)$, given for each data
    model.}
\newcommand{\powerDispersionProbCaption}[2]{
    The tendency of model #2 to support one divergence event when there is
    random variation in divergence times as simulated under the series of
    models #1.
    The plots illustrate histograms of the estimated posterior probability of
    the one divergence model, $p(\divTimeDispersion < 0.01 | \ssSpace)$, from
    analyses of 1000 datasets simulated under each of the #1 models, with the
    the estimated probability of the model strongly supporting one divergence
    event, $p(BF_{\divTimeDispersion < 0.01, \divTimeDispersion \geq 0.01} >
    10)$, given for each data model.}
\newcommand{\simulationDescription}[2]{\change{Each plot represents #1
    simulation replicates using the same $#2$ samples from the prior}}
\newcommand{\simulationDistribution}{\ensuremath{\divt{} \sim U(0,
    \divt{max})}\xspace}
\newcommand{\estimateDescription}[2]{All estimates were obtained using #1 and #2}
\newcommand{\estimateDescriptionUncorrected}[1]{All estimates based on
    unadjusted posterior, \truncprior{}, obtained using #1}
\newcommand{\priorDescription}[4]{Prior settings were \priorSettings{#1}{#2}{#3}{#4}}
\newcommand{\priorSettings}[4]{$\divt{} \sim U(0, #1)$,
    $\meanDescendantTheta{} \sim U(#2, #3)$, and
    $\ancestralTheta{}{} \sim U(#2, #4)$}
\newcommand{\priorDescriptionBug}[4]{Prior settings were
    \priorSettingsBug{#1}{#2}{#3}{#4}}
\newcommand{\priorSettingsBug}[4]{$\divt{} \sim U(0, #1)$,
    $\meanDescendantTheta{} \sim U(#2, #3)$, and
    $\ancestralTheta{}{} \sim U(0.01, #4)$}
\newcommand{\simulationScheme}{simulations where \divt{} (in \globalcoalunit
    generations) for 22 population pairs is drawn from a series of uniform
    distributions, \simulationDistribution}
\newcommand{\captionPowerOmega}{Histograms of the estimated dispersion index
    of divergence times ($\hat{\vmratio{}}$) from \simulationScheme.
    The threshold for one divergence event \citep{Hickerson2006} is indicated
    by the dashed line, and the estimated probability of inferring one
    divergence event, $p(\hat{\vmratio{}}\le 0.01)$, is given for each
    \divt{max}}
\newcommand{\captionPowerPsiMode}{Histograms of the estimated number of
    divergence events ($\hat{\numt{}}$) from \simulationScheme.
    The estimated probability of inferring one divergence event,
    $p(\hat{\numt{}} = 1)$, is given for each \divt{max}}
\newcommand{\captionPowerPsi}{Histograms of the estimated posterior
    probability of one divergence event, \postprobnumt{1}, from
    \simulationScheme.
    The estimated probability of inferring one divergence event with a
    Bayes factor greater than 10 (dashed black line),
    $p(\bayesfactor{\numt{}=1}{\numt{} \ne 1} > 10)$, is given for each \divt{max}.
    The red line indicates $\postprobnumt{1} = 0.95$, and the estimated
    probability of inferring a posterior probability greater than 0.95 is given
    to the right of the line.}
\newcommand{\captionAccuracy}[1]{Accuracy and precision of #1 estimates from
    \simulationScheme.
    The proportion of estimates less than the true value ($p(\hat{#1}<#1)$) is
    given for each \divt{max}}
\newcommand{\samplingErrorTableNote}{An estimate of 1.0 for a posterior probability
    is an artifact of sampling error}
